Results_paper1

### 2019-04-15 Paper1_results.Rmd
updated

# LOading the wind data
library(tidyverse)
library(circular)
wind_data <- read_csv("wind_data.csv", col_types = cols(X1 = col_number(), date = col_character(), dir = col_number(), hour = col_number(),  speed = col_number()))

wind_daily <- wind_data %>% 
  mutate(date = as.Date(date))%>%
   group_by(temp_sites, date) %>%
   summarise(dir_circ = round(mean.circular(circular(dir, units = "degrees")),2),
             mean_speed = round(mean(speed),2))

>>>>

# LOading the wind data
library(tidyverse)
library(circular)

# wind_data <- read_csv("wind_data.csv", col_types = cols(X1 = col_number(), date = col_character(), dir = col_number(), hour = col_number(),  speed = col_number())) # Dataset too large for Github but better data at line 638
# 
# wind_daily <- wind_data %>% 
#   mutate(date = as.Date(date))%>%
#    group_by(temp_sites, date) %>%
#    summarise(dir_circ = round(mean.circular(circular(dir, units = "degrees")),2),
#              mean_speed = round(mean(speed),2))
